### 2020-03-05 cv/cv-body.tex
Fix link
Update CV
Update cv

@@

Dory increase demand for blue tang fish? In press at Ambio.

@@

population aggregates. In press at Ecological Applications.

@@

\url{https://doi.org/10.32614/RJ-2019-007}.

@@

B.S. Halpern. Uncertainty in a global fisheries indicator. In press at
Fish and Fisheries.

@@

environmental, regulatory, and economic pressures. In press at Fish and
Fisheries. \url{https://doi.org/10.1111/faf.12364}.

>>>>

\item[2020]
Huynh, Q.C., A.R. Hordyk, R.E. Forrest, C.E. Porch, \textbf{S.C.
Anderson}, T.R. Carruthers. The interim management procedure approach
for assessed stocks: Responsive management advice and lower assessment
frequency. In press at Fish and Fisheries.
\url{https://doi.org/10.1111/faf.12453}.
\item[2020]
Free, C.M., O.P. Jensen, \textbf{S.C. Anderson}, N.L. Gutierrez, K.M.
Kleisner, C. Longo, C. Minto, G.C. Osio, J.C. Walsh. Blood from a stone:
performance of catch-only methods in estimating stock biomass status.
Fisheries Research. 223:105452.
\url{https://doi.org/10.1016/j.fishres.2019.105452}.
\item[2020]

@@

Dory increase demand for blue tang fish? Ambio. 49:903--911.

@@

population aggregates. Ecological Applications. 29(7):e01966.

@@

\href{https://journal.r-project.org/archive/2019/RJ-2019-007/RJ-2019-007.pdf}{https://doi.org/10.32614/RJ-2019-007}.

@@

B.S. Halpern. Quantifying uncertainty in the wild-caught fisheries goal
of the Ocean Health Index. Fish and Fisheries. 20(2):343--354.
\url{https://doi.org/10.1111/faf.12346}.

@@

environmental, regulatory, and economic pressures. Fish and Fisheries.
20(4):601--619. \url{https://doi.org/10.1111/faf.12364}.
